Local PCA results

### 2016-05-13 medicago/summarize_run.Rmd
multi-file vcf querying

@@

Here are the extreme windows in the MDS plot:
```{r get_corners}
mds.corners <- corners( mds.coords[,mds.cols[1:2]], prop=.05 )
# set up colors and pchs for corners
corner.cols <- brewer.pal(3,"Dark2")
corner.pch <- c(15,17,19)
ccols <- rep("black",nrow(mds.coords))
cpch <- rep(20,nrow(mds.coords))
for (k in 1:ncol(mds.corners)) {
    ccols[ mds.corners[,k] ] <- corner.cols[k]
    cpch[ mds.corners[,k] ] <- corner.pch[k]
}
# plot corners and MDS along the chromosome
layout(matrix(c(1,1,2,3),nrow=2),widths=c(1,2))
plot( mds.coords[,mds.cols[1:2]], pch=cpch, 
     col=adjustcolor(ccols,0.75), 
     xlab="MDS coordinate 1", ylab="MDS coordinate 2" )
for (k in mds.cols) {
    chrom.plot( mds.coords[,k], pch=20, 
            xlab="Position (Mb)", main=paste("MDS coordinate",match(k,mds.cols)),
            ylab=colnames(mds.coords)[k],
            col=adjustcolor(ccols,0.75) )
}
```

>>>>

# original data files
chroms <- paste0("chr",1:8)
bcf.files <- file.path( "..", "..", "data", paste0(chroms,"-filtered-set-2014Apr15.bcf") )
names(bcf.files) <- chroms

@@

Here are the extreme windows in the MDS plot:
```{r get_corners}
mds.corners <- corners( mds.coords[,mds.cols[1:2]], prop=.05 )
# set up colors and pchs for corners
corner.cols <- brewer.pal(3,"Dark2")
corner.pch <- c(15,17,19)
ccols <- rep("black",nrow(mds.coords))
cpch <- rep(20,nrow(mds.coords))
for (k in 1:ncol(mds.corners)) {
    ccols[ mds.corners[,k] ] <- corner.cols[k]
    cpch[ mds.corners[,k] ] <- corner.pch[k]
}
```
```{r plot_corners, fig.width=3*fig.dim}
# plot corners and MDS along the chromosome
layout(matrix(c(1,1,2,3),nrow=2),widths=c(1,2))
plot( mds.coords[,mds.cols[1:2]], pch=cpch, 
     col=adjustcolor(ccols,0.75), 
     xlab="MDS coordinate 1", ylab="MDS coordinate 2" )
for (k in mds.cols) {
    chrom.plot( mds.coords[,k], pch=20, 
            xlab="Position (Mb)", main=paste("MDS coordinate",match(k,mds.cols)),
            ylab=colnames(mds.coords)[k],
            col=adjustcolor(ccols,0.75) )
}
```

Now, we'll look at PCA plots from the extracted corners.
```{r corner_pca, cache=TRUE}
corner.regions <- lapply( 1:ncol(mds.corners), function (k) {
                regions[ mds.corners[,k], ]
    } )
corner.pca <- lapply( corner.regions, function (reg) {
            geno <- do.call( rbind, tapply( 1:nrow(reg), reg$chrom, function (k) {
                        chrom <- reg$chrom[k[1]]
                        vcf_query( bcf.files[chrom], reg[k,] )
                }, simplify=FALSE ) )
            cov_pca(geno,k=4)
    } )
```
